To prove that \eqref{eq:system4} constitutes the necessary and sufficient optimality conditions, we use Theorem 12.1 \cite{NW}. Since it is hard to know if LICQ holds in this case, we instead use another possible constraint qualification that is neither weaker nor stronger than LICQ. It says that the condition that all active constraints are linear, is enough. 

Because the function $g(\bm{q},\bm{f}^{\textrm{supp}})$ and the constraints in \eqref{eq:system5} are continuously differentiable, the requirements for Thm 12.1 are met.

By using the first of the KKT-conditions,
\begin{equation}
\nabla_{x}\mathcal{L}(x^{\ast},\lambda^{\ast}) = 0,
\end{equation}
for both of the variables, namely $\bm{q}$ and $\bm{f}^{\textrm{supp}}$, we get two equations:
\begin{equation}
\begin{aligned}
\nabla_{\bm{q}}\mathcal{L}(\bm{q}^{\ast},\lambda^{\ast}) = \nabla_{\bm{q}}g(\bm{q^{\ast}}) - \sum_{i\epsilon\mathcal{A}(\bm{q}^{\ast})}\lambda_{i}^{\ast}\nabla_{\bm{q}}c_{i}(\bm{q}^{\ast}) \\
\nabla_{\bm{f}^{\textrm{supp}}}\mathcal{L}(\bm{f}^{\textrm{supp}^{\ast}}, \lambda^{\ast}) = \nabla_{\bm{q}}g(\bm{f}^{\textrm{supp}^{\ast}}) - \sum_{i\epsilon\mathcal{A}(\bm{f}^{\textrm{supp}^{\ast}})}\lambda_{i}^{\ast}\nabla_{\bm{f}^{\textrm{supp}}}c_{i}(\bm{f}^{\textrm{supp}^{\ast}}).\\
\end{aligned}
\end{equation}

This leads to the two equations:

\begin{equation}
\begin{aligned}
\bm{Dq} = \bm{B}^{T}\lambda\\
\bm{I}^{T}_{\textrm{supp}}\lambda = 0
\end{aligned}
\end{equation}

By choosing $\lambda$ to be $\bm{u}$ we see that the KKT-conditions for \eqref{eq:system5} and the system \eqref{eq:system4} are equivalent, which is what we aimed to prove. Thm 12.1 is, however, only for proving necessary conditions, but since the KKT-conditions are sufficient under convexity, we can prove it is sufficient as well. For this to be true, $g(\bm{q},\bm{f}^{\textrm{supp}})$ must be convex and $c_{i}$ affine. The first requirement holds since we have a quadratic function. Because the $c_{i}$'s are linear functions, they are both convex and concave (affine). Hence we have proved that system \eqref{eq:system4} constitutes the necessary and sufficient optimality conditions for \eqref{eq:system5}.